Supplementary Materials for Characterization of the microbial and fungal communities in ancient pottery from Neolithic southwestern China

### 2024-02-05 analysis/supplementary-materials/Supplement.qmd
work on supplement

# pairwise t-test on richness
library(rstatix)
# no correction for the Type I error rate across the pairwise tests
rich_pair_V4 <- pairwise_t_test(V4_alphadiv, S.obs ~ group, p.adjust.method = 'none')
rich_pair_V1 <- pairwise_t_test(V1_alphadiv, S.obs ~ group, p.adjust.method = 'none')
rich_pair_V6 <- pairwise_t_test(V6_alphadiv, S.obs ~ group, p.adjust.method = 'none')
rich_pair_ITS1 <- pairwise_t_test(ITS1_alphadiv, S.obs ~ group, p.adjust.method = 'none')

# function to add region name
rich_pair_region <- function(df, vector) {
  df %>%
    mutate(region = vector) %>% 
    select(region, group1, group2, n1, n2, p, p.signif)
}

@@

kable(rich_pair_all , caption = "Table S1: Pairwise comparison of Richness index (the number of observed OTUs) using ANOVA")
```

```{r}
#| label: alpha-shannon
#| echo: false
#| cache: true
# pairwise t-test on Shannon

shan_pair_V4 <- pairwise_t_test(V4_alphadiv, shannon ~ group, p.adjust.method = 'none')
shan_pair_V1 <- pairwise_t_test(V1_alphadiv, shannon ~ group, p.adjust.method = 'none')
shan_pair_V6 <- pairwise_t_test(V6_alphadiv, shannon ~ group, p.adjust.method = 'none')
shan_pair_ITS1 <- pairwise_t_test(ITS1_alphadiv, shannon ~ group, p.adjust.method = 'none')

# function to add region name
shan_pair_region <- function(df, vector) {
  df %>%
    mutate(region = vector) %>% 
    select(region, group1, group2, n1, n2, p, p.signif)
}

@@

kable(shan_pair_all  , caption = "Table S2: Pairwise comparison of Shannon diversity indices using ANOVA")

```

>>>>

# pairwise Wilcoxon rank-sum  on richness and shannon
library(rstatix)

rich_pair_V4 <- V4_alphadiv %>% pairwise_wilcox_test(S.obs ~ group, p.adjust.method = 'fdr')
rich_pair_V1 <- V1_alphadiv %>% pairwise_wilcox_test(S.obs ~ group, p.adjust.method = 'fdr')
rich_pair_V6 <- V6_alphadiv %>% pairwise_wilcox_test(S.obs ~ group, p.adjust.method = 'fdr')
rich_pair_ITS1 <- ITS1_alphadiv %>% pairwise_wilcox_test(S.obs ~ group, p.adjust.method = 'fdr')

# function to add region name
rich_pair_region <- function(df, vector) {
  df %>%
    mutate(region = vector) %>% 
    select(region, group1, group2, n1, n2, p, p.adj, p.adj.signif)
}

@@

kable(rich_pair_all , caption = "Table S1: Pairwise comparison of Richness index (the number of observed OTUs) using Wilcoxon rank-sum test with FDR-adjusted p-value")
```

```{r}
#| label: alpha-shannon
#| echo: false
#| cache: true

# pairwise t-test on Shannon
shan_pair_V4 <- V4_alphadiv %>% pairwise_wilcox_test(shannon ~ group, p.adjust.method = 'fdr')
shan_pair_V1 <- V1_alphadiv %>% pairwise_wilcox_test(shannon ~ group, p.adjust.method = 'fdr')
shan_pair_V6 <- V6_alphadiv %>% pairwise_wilcox_test(shannon ~ group, p.adjust.method = 'fdr')
shan_pair_ITS1 <- ITS1_alphadiv %>% pairwise_wilcox_test(shannon ~ group, p.adjust.method = 'fdr')

# function to add region name
shan_pair_region <- function(df, vector) {
  df %>%
    mutate(region = vector) %>% 
    select(region, group1, group2, n1, n2, p, p.adj, p.adj.signif)
}

@@

kable(shan_pair_all  , caption = "Table S2: Pairwise comparison of Shannon diversity indices using Wilcoxon rank-sum test with FDR-adjusted p-value")
```
